Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s01_introduction.tex
Completed DRP example 2. Assembled recomb image. Got different images for intro and cleaned up tex file.

@@

Examples of such materials (See Figure \ref{examples}) include:

\begin{enumerate}
  %
    \item (cross-section) of microtubules \cite{Necklace1} e.g., in
ciliary membranes and transitions \cite{Necklace2}
   %
    \item (cross-section) of hierarchical bone structure \cite{XX} %
    \item crosslinked cellulose or collagen microfibril monolayers e.g.,
in cell-walls \cite{CellWalls1} \cite{CellWalls1}, as well as crosslinked
actin filaments in the cytoskeleton matrix.
  %
    \item more recent, engineered examples including  disordered graphene
layers \cite{Graphene1} \cite{Graphene2} sometimes reinforced
    by  microfibrils; and DNA assemblies \cite{Microfibrils1} including a
recent Sierpinski carpet, bringing other self-similar structures
    \cite{Microfibrils2} within reach.
    %
    \item  silica bi-layers, glass \cite{SilicaGlass1}
\cite{SilicaGlass2}, and materials that behave like assemblies of
    2D particles under non-overlap constraints, e.g, jammed
    disks on the plane \cite{JammedDisk1}
%
\end{enumerate}
%
In order to study structural and mechanical properties
such as rigidity, flexes and distribution of external stresses
within the material layer, it is natural to model a material
layer as a solution of a geometric constraint system
of appropriate types of geometric primitives, under
metric or algebraic constraints.
Such  2D {\bf{\em qusecs}} (quasi-uniform or self-similar
constraint systems) can be used to
understand or design material layers (their solutions)
with desired properties.
%
\subsection{Previous Work on Relevant 2D Geometric Constraint Systems} We
now briefly survey existing techniques for studying 2D {\em qusecs,}  many
of which are {\it bar-joint} systems (Examples 1,2 above, see Sections
\ref{sec:DRP}, \ref{sec:recomb}),
{\it multibody-pin} systems (Example 4,5, see Section \ref{sec:bodypin}) or  {\it
pinned-line incidence} systems (Example 3, see Section \ref{sec:pinnedline}). The
limitations of these techniques directly motivate
the contributions of this paper.

\medskip\noindent\underbar{{\sl (i) Finding (vertex)-maximal
generically rigid subsystems}}
Fast, graph-based algorithms exist (pebble-game \cite{XX}),
for locating all maximal, generically rigid subsystems \cite{XX}.
When the input is rigid, these algorithms compute the identity and  output
the input.

@@

\medskip\noindent\underbar{{\sl (ii) Optimal Recursive Decomposition
(DR-planning)}}
Recursive decomposition of geometric constraint systems has been
formalized \cite{XX} and well-studied \cite{XX}
as the {\sl Decomposition-Recombination (DR)-planning} problem.
For the above-mentioned classes of 2D qusecs, generic rigidity is
a combinatorial property and hence each level of the decomposition should,
in principle, be achievable by a graph-based algorithm as in (1), without
involving geometric information in the constraint system.
Since many  such decompositions can exist for a given constraint system,
criteria defining desirable or optimal DR-plans and DR-planning algorithms
were given in \cite{XX}. An {\em optimal DR-plan} is one
that minimizes the maximum number of child subsystems of any parent
system, a property that is
crucial for obtaining a solution to the parent constraint system from the
solutions of the child systems.

@@

\medskip\noindent\underbar{{\sl (iii) DR-plans for special classes and
with other criteria}}
For a special class of 2D qusecs, namely  {\em tree-decomposable} systems
\cite{XX} common in computer aided mechanical design,
(which includes ruler-and-compass and Henneberg-I constructible systems),
all DR-plans turn out to
be optimal. This satisfies the so-called {\em Church-Rosser} criterion,
leading to highly efficient DR-planning algorithms.
For general 2D qusecs, alternate criteria were suggested
such as {\em cluster minimality}
requiring parent systems to be composed of
a minimal set of at least 2 rigid proper subsystems (i.e., no proper
subset forms a rigid system);
and {\em proper maximality}, requiring child subsystems
to be maximal rigid proper subsystems of the parent system.

While polynomial time algorithms were given \cite{XX} to generate DR-plans
meeting the cluster minimality criterion,
no such algorithm is known for the latter criterion.

\medskip\noindent\underbar{{\sl (iv) Optimal Recombination and Solution
Space Navigation}}
For the entire DR-plan, finding all
desired solutions is barely tractable even if recombination
of solved subsystems is easy for each indecomposable parent system in the
DR-plan.
This is because even for the simplest, highly decomposable systems
with small DR-plans, the problem of finding even a single
solution to the input system at the root of the DR-plan
is NP-hard \cite{XX} and there is a
combinatorial explosion of solutions \cite{XX}. Typically, however,
the desired solution has a given orientation type, in which case,
the crux of the difficulty is concentrated in the algebraic complexity of
(re)combining child system solutions, to give a
solution to the parent system at any
given level of the DR-plan.
For fairly general 3D constraint systems,
there are algorithms with formal
guarantees that uncover underlying matroids to combinatorially
obtain an optimal parameterization to minimize the algebraic
complexity of the indecomposable parent (sub)systems that occur in the
DR-plan \cite{XX, XX,XX},
provided the DR-plan meets some of the abovementioned criteria.

@@

\medskip\noindent\underbar{{\sl (v) Configuration Spaces of
Underconstrained Systems}}
For underconstrained 2D bar-joint and multibody-pin cusecs obtained from
various subclasses of tree-decomposable systems, algorithms have been
developed \cite{XX, XX} that
to complete them into isostatic systems \cite{XX, XX} and to find paths
within the connected components \cite{XX,XX} of
standard cartesian configuration spaces. Most of the algorithms with
formal guarantees leverage Cayley configuration space theory \cite{XX,XX}
to characterize subclasses of graphs and additional constraints that
control combinatorial explosion, and provide faithful bijective
representation
of connected components and paths.
These algorithms have decreasing efficiency as the subclass of systems
gets bigger,  with highest efficiency for
underlying partial 2-tree graphs (alternately, tree-width 2,
series-parallel, $K_4$ minor avoiding),   moderate efficiency for
1 degree-of-freedom (dof) graphs with low Cayley complexity (which include
common linkages such as the Strandbeest, Limacon and Cardioid), and
decreased efficiency for general 1-dof tree-decomposable graphs. While
software suites exist \cite{XX,XX}, no such formal algorithms and
guarantees are known for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}
The contributions of this paper are the following.
\begin{itemize}
\item
We  navigate the NP-hardness barrier mentioned in (2) above, for finding
optimal DR-plans by defining a
so-called {\it canonical} DR-plan and showing a strong Church-Rosser
property: {\it all canonical DR-plans for isostatic or
underconstrained
2D qusecs are optimal} (Section \ref{sec:DRP}).
\item
We give an efficient ($O(n^2)$) algorithm to find a canonical (and hence
optimal) DR-plan for all 3 types of 2D qusecs mentioned above (Sections
\ref{sec:DRP}, \ref{sec:bodypin}, and \ref{sec:pinnedline}.
The canonical DR-plan
illuminates the essence of the NP-hardness of finding optimal DR-plans for
overconstrained systems.
\item
We give a method to deal with the
algebraic complexity of recombining the realizations or
solutions of  child subsystems into a solution of the parent system.
Specifically, we define the problem of  minimally modifying the
indecomposable recombination system so that it becomes decomposable via a
 small DR-plan and yet preserves the original
solutions in an efficiently searchable manner. We show formal connection
to well known problems such as optimal completion of
underconstrained  systems  \cite{XX}.  When the required modifications
are bounded, we obtain new, efficient algorithms for
realizing both isostatic and underconstrained
qusecs by leveraging recent results about Cayley parameters in
\cite{XX,XX}  (Section \ref{sec:recomb}).
\item
We briefly describe applications of the above techniques to modeling,
analyzing and designing specific properties in 2D material layers.
For Examples 1,2 (achieving isostaticity, distribution of stresses in
self-similar, bar-joint systems); Example 3 (canonical and optimal
DR-plans for pinned line incidence systems \cite{XX}) and Examples 4,5
(boundary-conditions for achieving various desired properties
of multi-body  pin systems).

>>>>

\newcommand{\meeraheader}[2]{\medskip\noindent\underbar{{\sl (#1) #2}}}

@@

Examples of such materials (See Figure \ref{fig:material_examples})
include:

\begin{figure*}\centering
% \begin{subfigure}{.31\linewidth}\centering
%   \includegraphics[width=\linewidth]{img/Axopodium_Mikrotubuli}
%   \caption{Cross section of a Heliozoa's psuedopod, formed by a spiral structure of microtubules.}
%   % https://de.wikipedia.org/wiki/Mikrotubulus#mediaviewer/File:Axopodium_Mikrotubuli.jpg
%   \label{fig:material_examples:microtubule}
% \end{subfigure}\hfill
% \begin{subfigure}{.31\linewidth}\centering
%   \includegraphics[width=\linewidth]{img/Transverse_Section_Of_Bone}
%   \caption{Cross section of an osteon (the fundamental unit of compact bone) exhibiting its hierarchical structure.}
%   % https://en.wikipedia.org/wiki/Osteon#mediaviewer/File:Transverse_Section_Of_Bone.png
%   \label{fig:material_examples:osteon}
% \end{subfigure}\hfill
\begin{subfigure}{.28\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Chlamydomonas_TEM_17}
  \caption{Cross section of the Chlamydomonas algae axoneme, a cilia composed of microtubules.}
  % https://en.wikipedia.org/wiki/Axoneme#mediaviewer/File:Chlamydomonas_TEM_17.jpg
  \label{fig:material_examples:microtubule}
\end{subfigure}\hfill
\begin{subfigure}{.40\linewidth}\centering
  \includegraphics[width=\linewidth]{img/ligten2}
  \caption{Cross section of a tendon displaying the hierarchical structure.}
  % http://www.umich.edu/~bme332/ch10ligten/ligten2.jpg
  \label{fig:material_examples:tendon}
\end{subfigure}\hfill
\begin{subfigure}{.30\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Rothemund-DNA-SierpinskiGasket}
  \caption{A DNA array exhibiting the Sierpinski triangle.}
  % https://en.wikipedia.org/wiki/DNA_nanotechnology#mediaviewer/File:Rothemund-DNA-SierpinskiGasket.jpg
  \label{fig:material_examples:sierpinski}
\end{subfigure}
\caption{}\label{fig:material_examples}
\end{figure*}

\begin{enumerate}
    \item Cross-sections of microtubule structures (Figure \ref{fig:material_examples:microtubule}) \cite{Necklace1} e.g., in ciliary membranes and transitions \cite{Necklace2}

    \item Cross-sections of organic tissue with hierarchical structure, e.g. compact bone and tendon (Figure \ref{fig:material_examples:tendon}) \cite{XX}

    \item crosslinked cellulose or collagen microfibril monolayers e.g., in cell-walls \cite{CellWalls1} \cite{CellWalls1}, as well as crosslinked actin filaments in the cytoskeleton matrix.

    \item more recent, engineered examples including  disordered graphene layers \cite{Graphene1} \cite{Graphene2} sometimes reinforced by  microfibrils; and DNA assemblies \cite{Microfibrils1} including a recent Sierpinski carpet, bringing other self-similar structures \cite{Microfibrils2} within reach.

    \item  silica bi-layers, glass \cite{SilicaGlass1} \cite{SilicaGlass2}, and materials that behave like assemblies of 2D particles under non-overlap constraints, e.g, jammed disks on the plane \cite{JammedDisk1}
\end{enumerate}
%
In order to study structural and mechanical properties such as
rigidity, flexes and distribution of external stresses within the
material layer, it is natural to model a material layer as a solution
of a geometric constraint system of appropriate types of geometric
primitives, under metric or algebraic constraints. Such  2D {\bf{\em
qusecs}} (quasi-uniform or self-similar constraint systems) can be
used to understand or design material layers (their solutions) with
desired properties.
%
\subsection{Previous Work on Relevant 2D Geometric Constraint Systems}
We now briefly survey existing techniques for studying 2D {\em
qusecs,}  many of which are {\it bar-joint} systems (Examples 1,2
above, see Sections \ref{sec:DRP}, \ref{sec:recomb}), {\it multibody-
pin} systems (Example 4,5, see Section \ref{sec:bodypin}) or  {\it
pinned-line incidence} systems (Example 3, see Section
\ref{sec:pinnedline}). The limitations of these techniques directly
motivate the contributions of this paper.

\meeraheader{i}{Finding (vertex)-maximal generically rigid subsystems}
Fast, graph-based algorithms exist (pebble-game \cite{XX}), for
locating all maximal, generically rigid subsystems \cite{XX}. When the
input is rigid, these algorithms compute the identity and  output the
input.

@@

\meeraheader{ii}{Optimal Recursive Decomposition (DR-planning)}
Recursive decomposition of geometric constraint systems has been
formalized \cite{XX} and well-studied \cite{XX} as the {\sl
Decomposition-Recombination (DR)-planning} problem. For the above-
mentioned classes of 2D qusecs, generic rigidity is a combinatorial
property and hence each level of the decomposition should, in
principle, be achievable by a graph-based algorithm as in (1), without
involving geometric information in the constraint system. Since many
such decompositions can exist for a given constraint system, criteria
defining desirable or optimal DR-plans and DR-planning algorithms were
given in \cite{XX}. An {\em optimal DR-plan} is one that minimizes the
maximum number of child subsystems of any parent system, a property
that is crucial for obtaining a solution to the parent constraint
system from the solutions of the child systems.

@@

\meeraheader{iii}{DR-plans for special classes and with other
criteria}
For a special class of 2D qusecs, namely  {\em tree-decomposable}
systems \cite{XX} common in computer aided mechanical design, (which
includes ruler-and-compass and Henneberg-I constructible systems), all
DR-plans turn out to be optimal. This satisfies the so-called {\em
Church-Rosser} criterion, leading to highly efficient DR-planning
algorithms. For general 2D qusecs, alternate criteria were suggested
such as {\em cluster minimality} requiring parent systems to be
composed of a minimal set of at least 2 rigid proper subsystems (i.e.,
no proper subset forms a rigid system); and {\em proper maximality},
requiring child subsystems to be maximal rigid proper subsystems of
the parent system.

While polynomial time algorithms were given \cite{XX} to generate DR-
plans meeting the cluster minimality criterion, no such algorithm is
known for the latter criterion.

\meeraheader{iv}{Optimal Recombination and Solution Space Navigation}
For the entire DR-plan, finding all desired solutions is barely
tractable even if recombination of solved subsystems is easy for each
indecomposable parent system in the DR-plan. This is because even for
the simplest, highly decomposable systems with small DR-plans, the
problem of finding even a single solution to the input system at the
root of the DR-plan is NP-hard \cite{XX} and there is a combinatorial
explosion of solutions \cite{XX}. Typically, however, the desired
solution has a given orientation type, in which case, the crux of the
difficulty is concentrated in the algebraic complexity of
(re)combining child system solutions, to give a solution to the parent
system at any given level of the DR-plan. For fairly general 3D
constraint systems, there are algorithms with formal guarantees that
uncover underlying matroids to combinatorially obtain an optimal
parameterization to minimize the algebraic complexity of the
indecomposable parent (sub)systems that occur in the DR-plan \cite{XX,
XX,XX}, provided the DR-plan meets some of the abovementioned
criteria.

@@

\meeraheader{v}{Configuration Spaces of Underconstrained Systems}
For underconstrained 2D bar-joint and multibody-pin cusecs obtained
from various subclasses of tree-decomposable systems, algorithms have
been developed \cite{XX, XX} that to complete them into isostatic
systems \cite{XX, XX} and to find paths within the connected
components \cite{XX,XX} of standard cartesian configuration spaces.
Most of the algorithms with formal guarantees leverage Cayley
configuration space theory \cite{XX,XX} to characterize subclasses of
graphs and additional constraints that control combinatorial
explosion, and provide faithful bijective representation of connected
components and paths. These algorithms have decreasing efficiency as
the subclass of systems gets bigger,  with highest efficiency for
underlying partial 2-tree graphs (alternately, tree-width 2, series-
parallel, $K_4$ minor avoiding), moderate efficiency for 1 degree-
of-freedom (dof) graphs with low Cayley complexity (which include
common linkages such as the Strandbeest, Limacon and Cardioid), and
decreased efficiency for general 1-dof tree-decomposable graphs. While
software suites exist \cite{XX,XX}, no such formal algorithms and
guarantees are known for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}

The contributions of this paper are the following.
\begin{itemize}
\item
We navigate the NP-hardness barrier mentioned in (2) above, for
finding optimal DR-plans by defining a so-called {\it canonical} DR-
plan and showing a strong Church-Rosser property: {\it all canonical
DR-plans for isostatic or underconstrained 2D qusecs are optimal}
(Section \ref{sec:DRP}).

\item
We give an efficient ($O(n^2)$) algorithm to find a canonical (and
hence optimal) DR-plan for all 3 types of 2D qusecs mentioned above
(Sections \ref{sec:DRP}, \ref{sec:bodypin}, and \ref{sec:pinnedline}.
The canonical DR-plan illuminates the essence of the NP-hardness of
finding optimal DR-plans for overconstrained systems.

\item
We give a method to deal with the algebraic complexity of recombining
the realizations or solutions of  child subsystems into a solution of
the parent system. Specifically, we define the problem of  minimally
modifying the indecomposable recombination system so that it becomes
decomposable via a small DR-plan and yet preserves the original
solutions in an efficiently searchable manner. We show formal
connection to well known problems such as optimal completion of
underconstrained  systems  \cite{XX}.  When the required modifications
are bounded, we obtain new, efficient algorithms for realizing both
isostatic and underconstrained qusecs by leveraging recent results
about Cayley parameters in \cite{XX,XX}  (Section \ref{sec:recomb}).

\item
We briefly describe applications of the above techniques to modeling,
analyzing and designing specific properties in 2D material layers. For
Examples 1,2 (achieving isostaticity, distribution of stresses in
self-similar, bar-joint systems); Example 3 (canonical and optimal DR-
plans for pinned line incidence systems \cite{XX}) and Examples 4,5
(boundary-conditions for achieving various desired properties of
multi-body  pin systems).

### 2014-12-16 doc/GMP2015/s03_drp.tex
Added figures to intro. Updated tikz figs, put them in separate files.
Really added figures this time
Completed DRP example 2. Assembled recomb image. Got different images for intro and cleaned up tex file.

\begin{proof}
\textit{Forward direction:} Proof by contradiction. If the $C_i\cup C_j$ was well-constrained but $C_i\cup C_j \neq C$, we would have found a larger well-constrained proper subgraph containing them; namely, $C_i\cup C_j$ or something containing it. The two original subgraphs could not have been vertex-maximal proper.

@@

We now present two examples of non-tree-decomposable graphs that illustrate the two cases found in decomposition -- intersection on a well-constrained subgraph and intersection on a trivial subgraph.

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}\centering
  \begin{tikzpicture}[scale=2]
        \tikzstyle{v}=[draw, circle, minimum size=0.1cm, font=\footnotesize]
        \tikzstyle{c}=[draw, circle, inner sep=1.5, fill=black]
        \tikzstyle{e}=[]

        \node[c] (v1) at (0,0.866) [label={left,inner sep=.555}:$a_1$]{};
        \node[c] (v2) at (-1,-0.866) [label={below,inner sep=.555}:$a_2$]{};
        \node[c] (v3) at (1,-0.866) [label={above,inner sep=.555}:$a_3$]{};

        \node[c] (v4) at (0,0.577-.1) [label={left,inner sep=.555}:$b_1$]{};
        \node[c] (v5) at (-0.667,-0.577-.1) [label={below,inner sep=.555}:$b_2$]{};
        \node[c] (v6) at (0.667,-0.577-.1) [label={above,inner sep=.555}:$b_3$]{};

        \node[c] (v7) at (0,0.289-.2) [label={left,inner sep=.555}:$c_1$]{};
        \node[c] (v8) at (-0.333,-0.289-.2) [label={below,inner sep=.555}:$c_2$]{};
        \node[c] (v9) at (0.333,-0.289-.2) [label={above,inner sep=.555}:$c_3$]{};

        \tedge{v1}{v2}{solid}{}{};
        \tedge{v1}{v3}{solid}{}{};
        \tedge{v2}{v3}{solid}{}{};

        \tedge{v4}{v5}{solid}{}{};
        \tedge{v4}{v6}{solid}{}{};
        \tedge{v5}{v6}{solid}{}{};

        \tedge{v7}{v8}{solid}{}{};
        \tedge{v7}{v9}{solid}{}{};
        \tedge{v8}{v9}{solid}{}{};

        \tedge{v1}{v4}{solid}{}{};
        \tedge{v2}{v5}{solid}{}{};
        \tedge{v3}{v6}{solid}{}{};

        \tedge{v4}{v7}{solid}{}{};
        \tedge{v5}{v8}{solid}{}{};
        \tedge{v6}{v9}{solid}{}{};
    \end{tikzpicture}

    \caption{}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}\centering
    \begin{tikzpicture}[scale=.9, transform shape]
        \tikzstyle{v}=[draw, circle, minimum size=0.75cm, font=\footnotesize]
        % \tikzstyle{b}=[draw, font=\footnotesize]
        \tikzstyle{b}=[]
        \tikzstyle{e}=[]

        \node[b] (c0) at (0,0) {$\{a_1,a_2,a_3,b_1,b_2,b_3,c_1,c_2,c_3\}$};
        \node[b] (c1a) at (-2,-1) {$\{a_1,a_2,a_3,b_1,b_2,b_3\}$};
        \node[b] (c1b) at (2,-1) {$\{b_1,b_2,b_3,c_1,c_2,c_3\}$};
        \node[b] (c2a) at (-2,-2) {$\{a_1,a_2,a_3\}$};
        \node[b] (c2b) at (0,-2) {$\{b_1,b_2,b_3\}$};
        \node[b] (c2c) at (2,-2) {$\{c_1,c_2,c_3\}$};
        \node[b] (c2ab1) at (-5.6,-2) {$\{a_1,b_1\}$};
        \node[b] (c2ab2) at (-4.5,-2) {$\{a_2,b_2\}$};
        \node[b] (c2ab3) at (-3.4,-2) {$\{a_3,b_3\}$};
        \node[b] (c2bc1) at (5.6,-2) {$\{b_1,c_1\}$};
        \node[b] (c2bc2) at (4.5,-2) {$\{b_2,c_2\}$};
        \node[b] (c2bc3) at (3.4,-2) {$\{b_3,c_3\}$};

        \tedge{c0}{c1a}{solid}{}{};
        \tedge{c0}{c1b}{solid}{}{};

        \tedge{c1a}{c2ab1}{solid}{}{};
        \tedge{c1a}{c2ab2}{solid}{}{};
        \tedge{c1a}{c2ab3}{solid}{}{};
        \tedge{c1a}{c2a}{solid}{}{};
        \tedge{c1a}{c2b}{solid}{}{};

        \tedge{c1b}{c2bc1}{solid}{}{};
        \tedge{c1b}{c2bc2}{solid}{}{};
        \tedge{c1b}{c2bc3}{solid}{}{};
        \tedge{c1b}{c2b}{solid}{}{};
        \tedge{c1b}{c2c}{solid}{}{};
    \end{tikzpicture}

    \caption{}
\end{subfigure}

\caption{(a) Two doublets ($C2\times C3$), $\{a_1,a_2,a_3,b_1,b_2,b_3\}$ and $\{b_1,b_2,b_3,c_1,c_2,c_3\}$, intersecting on the triangle $\{b_1,b_2,b_3\}$. (b) The optimal DR-plan of the graph if we consider it to be a 2D graph; omits further decomposition of the three triangles into their edges and of edges into their individual nodes.}
\label{doublets}
\end{figure*}

\begin{example}
    In figure \ref{doublets}, the two well-constrained vertex-maximal proper subgraphs of the graph are the two doublets, shown in the second level of the DR-plan. These intersect on the well-constrained graph $\{b_1,b_2,b_3\}$. This will necessarily be a child $N=2$ levels below the parent of the two doublets, as explained in Theorem \ref{theorem:main_wellconstrained}. Also shown is the decomposition of the individual doublets. These have five well-constrained vertex-maximal proper subgraphs, the two triangles and the three edges connecting them. As explained in Theorem \ref{theorem:main_trivial}, all of them must be included in the optimal DR-plan. Were any left out, the union of the children would not be the entire parent.
\end{example}

\begin{figure*}\centering
\begin{tikzpicture}[scale=3]
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{c}=[draw, circle, inner sep=1.5, fill=black]
    \tikzstyle{e}=[]

    \node[circle,fill=white,inner sep=7] (center) at (0,0-.125-.1) {};

    \node[c] (v1) at (0,0.866) [label={left,inner sep=.555}:$a_1$]{};
    \node[c] (v2) at (-1,-0.866) [label={below,inner sep=.555}:$a_2$]{};
    \node[c] (v3) at (1,-0.866) [label={above,inner sep=.555}:$a_3$]{};

    \node[c] (v4) at (0,0.433-.125) [label={left,inner sep=.555}:$b_1$]{};
    \node[c] (v5) at (-0.5,-0.433-.125) [label={below,inner sep=.555}:$b_2$]{};
    \node[c] (v6) at (0.5,-0.433-.125) [label={above,inner sep=.555}:$b_3$]{};

    \tedge{v1}{v2}{solid}{}{};
    \tedge{v1}{v3}{solid}{}{};
    \tedge{v2}{v3}{solid}{}{};

    \tedge{v4}{v5}{solid}{}{};
    \tedge{v4}{v6}{solid}{}{};
    \tedge{v5}{v6}{solid}{}{};

    \tedge{v1}{v4}{solid}{}{};
    \tedge{v2}{v5}{solid}{}{};
    \tedge{v3}{v6}{solid}{}{};

    \tedge{v4}{center}{dashed}{}{};
    \tedge{v5}{center}{dashed}{}{};
    \tedge{v6}{center}{dashed}{}{};

    % sin(30deg) = 0.5
    % cos(30deg) = 0.866

    % o/i -> outside/inside triangle
    % b/l/r -> bottom/left/right edge of triangle

    \coordinate (ob0) at (-0.333,-0.866-0.1);
    \coordinate (ob1) at (0.333,-0.866-0.1);
    \coordinate (ob2) at (-0.333,-0.866+0.1);
    \coordinate (ob3) at (0.333,-0.866+0.1);
    \draw (v2) -- (ob0) -- (ob1) -- (v3);
    \draw (v2) -- (ob2) -- (ob3) -- (v3);
    \draw (ob0) -- (ob3);
    \draw (ob2) -- (ob1);

    \draw[rotate around={60:(-1,-0.866)}] (v2) -- (-0.333,-0.766) -- (0.333,-0.766) -- (v1);
    \draw[rotate around={60:(-1,-0.866)}]  (v2) -- (-0.333,-0.966) -- (0.333,-0.966) -- (v1);
    \draw[rotate around={60:(-1,-0.866)}]  (-0.333,-0.766) -- (0.333,-0.966);
    \draw[rotate around={60:(-1,-0.866)}]  (-0.333,-0.966) -- (0.333,-0.766);

    \draw[rotate around={-60:(1,-0.866)}] (v3) -- (0.333,-0.766) -- (-0.333,-0.766) -- (v1);
    \draw[rotate around={-60:(1,-0.866)}]  (v3) -- (0.333,-0.966) -- (-0.333,-0.966) -- (v1);
    \draw[rotate around={-60:(1,-0.866)}]  (-0.333,-0.766) -- (0.333,-0.966);
    \draw[rotate around={-60:(1,-0.866)}]  (-0.333,-0.966) -- (0.333,-0.766);

    \coordinate (ib0) at (-0.167,-0.433-.125-0.1); %(-.167,-.658)
    \coordinate (ib1) at (0.167,-0.433-.125-0.1); %(.167,-.658)
    \coordinate (ib2) at (-0.167,-0.433-.125+0.1);%(-.167,-.458)
    \coordinate (ib3) at (0.167,-0.433-.125+0.1);%(.167,-.458)
    \draw (v5) -- (ib0) -- (ib1) -- (v6);
    \draw (v5) -- (ib2) -- (ib3) -- (v6);
    \draw (ib0) -- (ib3);
    \draw (ib2) -- (ib1);

    \draw[rotate around={60:(-0.5,-0.558)}] (v5) -- (-.167,-.658) -- (.167,-.658) -- (v4);
    \draw[rotate around={60:(-0.5,-0.558)}]  (v5) -- (-.167,-.458) -- (.167,-.458) -- (v4);
    \draw[rotate around={60:(-0.5,-0.558)}]  (-.167,-.658) -- (.167,-.458);
    \draw[rotate around={60:(-0.5,-0.558)}]  (-.167,-.458) -- (.167,-.658);

    \draw[rotate around={-60:(0.5,-0.558)}] (v6) -- (.167,-.658) -- (-.167,-.658) -- (v4);
    \draw[rotate around={-60:(0.5,-0.558)}]  (v6) -- (.167,-.458) -- (-.167,-.458) -- (v4);
    \draw[rotate around={-60:(0.5,-0.558)}]  (-.167,-.658) -- (.167,-.458);
    \draw[rotate around={-60:(0.5,-0.558)}]  (-.167,-.458) -- (.167,-.658);
% \newcommand{\tedge}[5]{\draw[#3] (#1)-- node[e, #5] (e#4) {#4} (#2)}

    % \draw (-1,-0.866) -- (-0.333,-0.966);

\end{tikzpicture}

\caption{A doublet with each edge replaced by a $K3,3$. \todo{Drawing incomplete.}}
\label{c2c3ofk33s}
\end{figure*}

\begin{example}
    In figure \ref{c2c3ofk33s}... \todo{Is it worth working through this? The first example has trivial and non-trivial.}
\end{example}

>>>>

\begin{proof}
%I wouldn't do the forward and backward direction italics, or say proof by contradiction. Just start the first paragraph with Suppose C_i union C_j is well constained maximal proper and assume it is not C.
\textit{Forward direction:} Proof by contradiction. If the $C_i\cup C_j$ was well-constrained but $C_i\cup C_j \neq C$, we would have found a larger well-constrained proper subgraph containing them; namely, $C_i\cup C_j$ or something containing it. The two original subgraphs could not have been vertex-maximal proper.

@@

We now present two examples of non-tree-decomposable graphs that illustrate the the strength and flexibility of the canonical DR-plan.

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}\centering
    \input{img/tikz/two_doublets-0.tikz}
    \caption{}\label{fig:doublets:a}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}\centering
    \input{img/tikz/two_doublets-1.tikz}
    \caption{}\label{fig:doublets:b}
\end{subfigure}

\caption{(\ref{fig:doublets:a}) Two doublets ($C2\times C3$), $\{a_1,a_2,a_3,b_1,b_2,b_3\}$ and $\{b_1,b_2,b_3,c_1,c_2,c_3\}$, intersecting on the triangle $\{b_1,b_2,b_3\}$. (\ref{fig:doublets:b}) The optimal DR-plan of the graph if we consider it to be a 2D graph; omits further decomposition of the three triangles into their edges and of edges into their individual nodes.}
\label{fig:doublets}
\end{figure*}

\begin{example}
    In figure \ref{fig:doublets}, the two well-constrained vertex-maximal proper subgraphs of the graph are the two doublets, shown in the second level of the DR-plan. These intersect on the well-constrained graph $\{b_1,b_2,b_3\}$. This will necessarily be a child $N=2$ levels below the parent of the two doublets, as explained in Theorem \ref{theorem:main}, point 2. Also shown is the decomposition of the individual doublets. These have five well-constrained vertex-maximal proper subgraphs, the two triangles and the three edges connecting them. As explained in Theorem \ref{theorem:main}, point 1, all of them must be included in the optimal DR-plan. Were any left out, the union of the children would not be the entire parent.
\end{example}

\begin{figure*}\centering
\begin{subfigure}{.3\linewidth}\centering
    \input{img/tikz/c2c3_of_k33s-0.tikz}
    \caption{}\label{fig:c2c3ofk33s:a}
\end{subfigure}%
\begin{subfigure}{.7\linewidth}\centering
    \input{img/tikz/c2c3_of_k33s-1.tikz}
    \caption{}\label{fig:c2c3ofk33s:b}
\end{subfigure}

\caption{(\ref{fig:c2c3ofk33s:a}) A doublet with each edge of the triangles replaced by a $K3,3$. This pattern continues for a total of $N$ triangles. (\ref{fig:c2c3ofk33s:b}) The DR-plan of this graph, omitting further decomposition of $K3,3$ subgraphs into the separate 9 edges and of edges into the component nodes. $G\setminus\{a_i,b_i,c_i\}$ is shorthand for $G$ difference those nodes and all of the nodes in the corresponding $K3,3$ subgraphs. The dashed lines indicated that this exact structure is repeated until only $\{a_{(N+1)/2},b_{(N+1)/2},c_{(N+1)/2}\}$ remains in the case that $N$ is odd, or until only $\{a_{N/2},b_{N/2},c_{N/2},a_{(N/2)+1},b_{(N/2)+1},c_{(N/2)+1}\}$ remains if $N$ is even.}
\label{fig:c2c3ofk33s}
\end{figure*}

% \begin{example}
%     In
% \end{example}
